### 2017-12-28 Paper/examples.tex
working on the borehole example

In this section, we motivate this approach based
on parameter screening to construct low-dimensional PC surrogates by 
applying it to simple test problems: (1) Borehole function, (2) Non-linear Oscillator, and
(3) Semi-linear Elliptic PDE. Since model evaluations in all these test
problems are not expensive, it allows us to compare relative importance of
model parameters,
obtained using the derivative-based sensitivity approach with that obtained
using converged estimates of Sobol' total effect sensitivity index~\cite{Sobol:2001}.
Additionally, we compare convergence of the PC Surrogates, constructed in
the full and the reduced space, based on the 
leave-one-out-cross-validation error ($\epsilon_{\mbox{\tiny LOO}}$), defined
as follows~\cite{Blatman:2010}:

@@

Since function evaluations of the discharge using Eq.~\ref{eq:bore} are quite cheap, the converged
estimates of Sobol' total effect sensitivity index can be easily computed.

>>>>

In this section, we motivate this approach based
on parameter screening to construct low-dimensional PC surrogates by 
applying it to simple test problems: (1) Borehole function, (2) Non-linear Oscillator, and
(3) Semi-linear Elliptic PDE. Since model evaluations in all these test
problems are not expensive, it allows us to compare relative importance of
model parameters,
obtained using the derivative-based sensitivity approach with that obtained
using converged estimates of Sobol' total effect sensitivity index, $\mathcal{T}(\theta_i)$~\cite{Sobol:2001}:

\be
\mathcal{T}(\theta_i) = 
\frac{\mathbb{E}_{\bm{\theta}\sim i}[\mathbb{V}_{\theta_i}(\mathcal{G}|\bm{\theta}_{\sim i})]}{\mathbb{V}(\mathcal{G})}
\ee

\noindent $\mathcal{T}(\theta_i)$ is essentially the ratio of the contribution to the variance of an
observable $\mathcal{G}$ by the parameter $\theta_i$ to the total variance of $\mathcal{G}$.
Additionally, we compare convergence of the PCE constructed in
the full parameter space with those constructed in the reduced space. To assess convergence, 
we rely on the 
leave-one-out-cross-validation error ($\epsilon_{\mbox{\tiny LOO}}$), defined
as follows~\cite{Blatman:2010}:

@@

As mentioned earlier in this section, cheap function evaluations of the discharge using 
Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
parameters in the borehole function.
